\documentclass[a4paper]{article}
\usepackage{latexsym}
\usepackage[a4paper]{geometry}
\usepackage{color}
\usepackage{listings}
\usepackage[pdftex]{graphicx}
\usepackage{subfig}

\definecolor{Blue}{rgb}{0,0,0.5}
\definecolor{Green}{rgb}{0,0.75,0.0}
\definecolor{LightGray}{rgb}{0.6,0.6,0.6}
\definecolor{DarkGray}{rgb}{0.3,0.3,0.3}
%\lstset{language=C++,
%   keywords={function,uint8,uint16,uint32,double,break,case,catch,continue,else,elseif,end,for,global,if,otherwise,persistent,return,switch,try,while},
%   basicstyle=\ttfamily\small,
%   breaklines=true,
%   keywordstyle=\bfseries\color{Blue},
%   commentstyle=\itshape\color{LightGray},
%   stringstyle=\color{Green},
%   numbers=left,
%   numberstyle=\tiny\color{DarkGray},
%   stepnumber=1,
%   numbersep=10pt,
%   backgroundcolor=\color{white},
%   tabsize=2,
%   showspaces=false,
%   showstringspaces=false,
%   captionpos=b}

%Boldface text for type writer font
\usepackage{bold-extra} %\DeclareFontShape{OT1}{cmtt}{bx}{n}{<5><6><7><8><9><10><10.95><12><14.4><17.28><20.74><24.88>cmttb10}{}

%Break words properly at the end of a line (which isn't sloppy...)
\sloppy

%Use command \exercise for each exercise
\newcounter{exerciseCount}
\setcounter{exerciseCount}{0}
\newcommand{\exercise}[1]{\addtocounter{exerciseCount}{1} \noindent \medskip {\large \textsf{\textbf{Exercise \arabic{exerciseCount} #1}}} \par}
\renewcommand{\theenumi}{\textsf{\textbf{\alph{enumi}}}}

%Use command \code for code snippets
\newcommand{\code}[1]{\textnormal{\texttt{#1}}}

\setlength{\parindent}{0in}

\title{\textsf{C/C++ Part I \\ Chapter 1 - Set One}}
\author{Christian Manteuffel \and Spyros Ioakeimidis}
\date{\today}

\begin{document}
\maketitle

\exercise{}

% not complete descriptions
\begin{description}
	\item[hello.cc] is the C++ source file. It contains \verb|#include|s, the \verb|main()|, and definitions. It is read by the compiler.
	\item[hello.o] is the object file, which is generated by the compiler. It contains external references, and definitions as instructions.
	\item[hello] is the executable program, which is generated at the linking phase.
\end{description}

\lstinputlisting[language=C++,caption={hello.cc},label=lis:1]{./src/hello.cc}


The source code in Listing~\ref{lis:1} has been compiled with the command \texttt{g++-4.7.1 -Wall --std=c++11 -c hello.cc} and subsequently linked to create an executable with \texttt{g++-4.7.1 -Wall --std=c++11 -o hello hello.o}.\\

The program produces the following output: 
\begin{verbatim}
Hello World
\end{verbatim}

The size of the source file \verb|hello.cc| is 69Bytes, the object file \verb|hello.o| is 1824Bytes and the executable \verb|hello| is 9300Byte large. After stripping the symbol tables, the executable is 8988Bytes large. The file \verb|iostream| has been found under \verb|/usr/gcc-4.7.1/include/c++/4.7.1| and is 2735Bytes large.\\

\exercise{}

We identified 13 basic data types, although \verb|size_t| is not really a built-in primitive data type.

\begin{verbatim}
void; char; short; int; long; float; double; bool; wchar_t; 
long long; long double; long long int; size_t
\end{verbatim}


\exercise{}
%spyros
\begin{description}
	\item[b / B] indicates a hexadecimal value, e.g.\ 0xb which is equal to decimal 11. It can also be used to define a binary constant, e.g. 0b1001 which is equal to the decimal value 9.
	\item[e / E] is the exponentiation character in floating point literal values. For example, 1.15E+2 represents the decimal value 115. It can also be used to indicate a hexadecimal value, e.g. 0xE which is equal to the decimal value 14.
	\item[f / F] can be used as a postfix to a non-integral numeric constant to indicate a value of type float. For example, 10.F is a float value. Another example is 1.155E+2F which is equal to the decimal value 115.5. It also indicates a hexadecimal value, e.g. 0xf which is equal to the decimal value 15.
	\item[L] can be used as a prefix to indicate a character string whose elements are wchar\_t type characters. For example, L"Hello, World!". It can also be used as a postfix to an integral value to indicate a value of type long, e.g. 20L.
	\item[p] is used to specify the power in hexadecimal floating point numbers. For example, 0x10p2 which is equal to the decimal value 64. The exponent itself is read as a decimal constant and can therefore not start with 0x.
	\item[u / U] can be used as postfix to an integral value to indicate an unsigned value. For example, 2U. It can also be combined with L to produce an unsigned long int value, e.g. 10UL. Alternatively, it can be used as a prefix to indicate various unicode encodings. For example:
	\begin{itemize}
		\item \verb|char     utf_8[ ] = u8"UTF-8 encoded";|
		\item \verb|char16_t utf16[ ] = u"UTF-16 encoded";|
		\item \verb|char32_t utf32[ ] = U"UTF-32 encoded";|
	\end{itemize}
	\item[x / X] is used in order to specify hexadecimal constants, e.g. 0x8 which is equal to the decimal value 8.
	\item[a / A] is used in order to specify a hexadecimal value, e.g. 0xA which is equal to the decimal value 10.
	\item[c / C] is used in order to indicate a hexadecimal value, e.g. 0xC which is equal to the decimal value 12.
	\item[d / D] is used in order to indicate a hexadecimal value, e.g. 0xD which is equal to the decimal value 13.
\end{description}

\exercise{}
%cm
The character \verb|a| is represented by the decimal value 97 in the ASCII -Table. Three times 97 will be larger than 256 and thus exceeds the size of the char datatype, which results in an implicit overflow $(3 * 97) \% 256$.

After the overflow the char has the decimal value 35 or the character representation \#.\\

\exercise{}
%spyros

The type of the parameters of the function \verb|showDate| are not well chosen and the design can be improved. As an alternative design we could have created an enumeration for the type of the month. The definition of the enumeration could be the following:

\begin{verbatim}
enum Months
{
    January=1, February, March, April, May, June, July,
    August, September, October, November, December
};
\end{verbatim}

Now the declaration of the function will be \verb|showDate(int daynr, Months month, int year)|, letting the user specify the name of the month instead of a decimal number, e.g. \verb|showDate(2, September, 2010)|. This leads to better readable and maintainable code.\\

There is no need to change the year, as it is perceived by definition an integer type. The same could be true for the number of the day of the month. However, in order to be able to generate the name of the day in the output, we assume that the function definition contains a way of accomplishing this.\\

\exercise{}
%cm

\begin{description}
	\item[Q1]\-
	%In C++, what's the difference between a declaration and a definition?
	A declaration introduces an identifier and describes its type, be it a type, object, or function. A declaration is what the compiler needs to accept references to that identifier.
	
	A definition actually instantiates/implements this identifier. It's what the linker needs in order to link references to those entities. A definition can be used in the place of a declaration.
%An identifier can be declared as often as you want. However, it must be defined exactly once. If we forget to define something that has been declared and referenced somewhere, then the linker does not know what to link references to and complains about missing symbols. If we define something more than once, then the linker does not know which of the definitions to link references to and complains about duplicated symbols.
	\item[Q2]\-
	%What are header files used for?
	To declare methods, variables constants, classes etc. It separates the declaration from the definition in the actual source code file. The purpose of a header file is to hold declarations for other files to use.
%Interface
	\item[Q3]\-
	%In what part of program development are header files used and in what part libraries? (Why are they used)?
	Header files are used mainly during the design phase of program development, as they only contain declarations. Header files are used mainly as interfaces.

	Libraries are used during the implementation phase of the program development. Libraries are meant to be used by other programs. 
	\item[Q4]\-
	%Is a library an object module? Explain and explain why they are used.
	Library is not an object module. It is a package of code. Typically it consists of a header file that contains declarations for everything the library wishes to expose, and a precompiled object that contains all of the implementation code compiled into machine language. Libraries are meant to be used by other programs.
	\item[Q5]\-
	%Why an object module obtained from compiling a source containing int main() is not an executable program?
	The compilation step and the creation of the object file does not create anything the user can actually run. Instead, the compiler merely produces the machine language instructions that correspond to the source code file that was compiled. An object file contains a translation of the source code file into a machine language file.
	%Another (more obvious) advantage is that this allows the creation of large programs without having to redo the compilation step every time a file is changed.
\end{description}

\exercise{}
%spyros

\begin{description}
	\item[Q1]\-
	The source file will always compile and without warnings. Even though in some cases the same integer numbers are used in order to define a company, this is not an issue for the compiler as long as the names of the companies remain unique. Furthermore, there is no issue with the declaration of the two functions.
	\item[Q2]\-
	There are ways to improve the provided source file. The problem with the use of the \verb|#define| preprocessor directives is that albeit there is a clear separation of the two different kind of companies, if we would want to add more companies, the list would increase too much. Furthermore, with the way the functions are declared, someone could pass a railroad company in the function which provides the schedule of airline companies and the compiler would not complain about it. However, the program could either crash or the results would be totally wrong.\\
	
	Therefore, we focus in two places where the source file could be improved. First is to turn the define lists of the companies into enumerations. Two separated enumerations could be created. One for each kind of company.
	
	\begin{verbatim}
	enum RailroadCompanies
	{
	    NS, DB, SNCF, BR, AMTRAK
	};
	
	enum AirlineCompanies
	{
	    BritishAirways, KLM, Lufthansa, UnitedAirlines
	};
	\end{verbatim}
	
	By creating these two enumerations, not only we completely remove the deprecated \verb|#define| preprocessor directives, but also the code becomes more maintainable and readable. And this because if in the future we would like to introduce additional companies of any kind, we could easily add them in the related enumeration. Also the values are generated automatically for us. Moreover, the use of enumerations offers the possibility of checking the values.\\
	
	The second improvement would be in the declaration of the two functions responsible for the schedules. As we previously introduced the enumerations, now we can change the declarations of these functions to the following:
	
	\begin{verbatim}
	void airlineSchedule(AirlineCompanies company);
	
	void railroadSchedule(RailroadCompanies company);
	\end{verbatim}
	
	These changes also lead to more maintainable and readable code. Furthermore, now it is clear which type of company each function expect. The call of one of these functions with an inappropriate company would lead to an error, e.g. calling the function \verb|railroadSchedule| with the company \verb|KLM|.
	\item[Q3]\-
	The header probably contains a definition of the variable with name \verb|DB|. The problem is the definition of the company \verb|DB| with the \verb|#define| preprocessor directive. If the header file is included in the first line of the source file then there will be no compile error, as the definition of \verb|DB| with \verb|#define| will overwrite the previous definition pf \verb|DB| in the header file.
	
	However, if the header file is included just before the function declarations, then at the time of the definition of \verb|DB| in the header file, an error will be generated because \verb|DB| has already been defined using a macro and its value is 1 and cannot change. This problem lies in the fact that macros ignore scopes, the type system, and the language's features and rules. The improvements that we introduced with the use of enumerations prevent the compilation errors.
	\item[Q4]\-
	This happens because the definition of \verb|DB| using the \verb|#define| directive overwrites the previous definition of it in the header file. Macros are visible from the time of their definition. Therefore, it is impossible to use \verb|DB| as whatever is defined as in the header file, because at the time of use of \verb|DB| in the source file, the preprocessor has already replaced \verb|DB| with the integer value 1.
	
	\verb|C++| offers an alternative with the use of the scope resolution operator \verb|::| and the concept of namespaces. For example, we could use \verb|DB| of the db header file like \verb|db::DB|, using the db namespace.
\end{description}

\exercise{}
%cm

Escape sequences can be used to invoke an alternative character in a string or char. This can be useful because certain characters are not represented by a symbol (e.g. newline or backspace) or they are used differently by the language (e.g. backslash or a question mark to create trigraphs).  In C++ escape sequences start with a \textbackslash  and are followed by one or more characters. Table~\ref{tab:escape} shows the available escape sequences in C++\footnote{Taken from ISO/IEC 14882-2011 and http://en.cppreference.com/w/cpp/language/escape}.

If an unknown character is written after the backslash, an error is thrown ``unknown escape sequence''. The program terminates.

\begin{table}[htdp]
\caption{Escape Sequences}
\begin{center}
\begin{tabular}{|ll|ll|}
\textbackslash'	 & single quote	 & \textbackslash"	  &double quote	  \\
\textbackslash?	 & question mark & \textbackslash\textbackslash& backslash	 \\
\textbackslash 0&  null character	& \textbackslash a&	 audible bell	 \\
\textbackslash b&	 backspace	& \textbackslash f	 &form feed - new page \\
\textbackslash n&	 line feed - new line & \textbackslash r	 &carriage return	 \\
\textbackslash t	 &horizontal tab	 & \textbackslash v&	 vertical tab	 \\
\textbackslash ooo&	 arbitrary octal value	  & \textbackslash xhhh	& arbitrary hexadecimal value	 \\
\textbackslash unnnn&	 arbitrary Unicode value & \textbackslash Unnnnnnnn&	 arbitrary Unicode value \\
\end{tabular}
\end{center}
\label{tab:escape}
\end{table}%



\end{document}
